Self Regulation Ontology Retest Analyses

### 2018-03-21 code/SRO_Retest_Analyses.Rmd
added sampling analysis in comparing the lit review to our results

```{r}
tmp  = rel_comp %>% filter(dv == unique(rel_comp$dv)[10])

@@

sample_from_dv(tmp)

sampled_df = rel_comp %>%
  group_by(dv) %>%
  do(sample_from_dv(.))

summary(lm(retest_reliability ~ lit_predictor, data=sampled_df))
summary(lm(retest_reliability ~ mean_icc, data=sampled_df))
```

>>>>

```{r}
comp_lit_pred <- function(df){

@@

  sampled_df = df %>%
    group_by(dv) %>%
    do(sample_from_dv(.))

  mod_lit = lm(retest_reliability ~ lit_predictor, data=sampled_df)
  mod_boot = lm(retest_reliability ~ mean_icc, data=sampled_df)

  out = data.frame(r2_lit = summary(mod_lit)$r.squared,
                   r2_boot = summary(mod_boot)$r.squared,
                   m_lit = coef(summary(mod_lit))["lit_predictor","Estimate"],
                   m_boot = coef(summary(mod_boot))["mean_icc","Estimate"])

  return(out)
}

comp_lit_pred_out = plyr::rdply(1000, comp_lit_pred(rel_comp))

comp_lit_pred_out %>%
  select(-.n) %>%
  gather(key, value) %>%
  separate(key, c("stat", "sample"), sep = "_") %>%
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity')+
  facet_wrap(~stat, scales='free')+
  theme(legend.title = element_blank())+
  xlab('')
```
